### 2019-10-10 tim-lucas-model-ensembles.tex
Fiull in table of mle. Using means over cv though.

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. Values outside 0.7--0.9 are shown in bold.}
\centering
\begin{tabular}{llrrrrr}
CV & Country &  Enviro & ML\textsubscript{l} &  Enviro + ML\textsubscript{l} & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random & \textbf{0.28} & \textbf{0.28} & \textbf{0.29} & \textbf{0.29} & \textbf{0.29} \\
 Madagascar &  Random & 0.80 & 0.77& 0.75& 0.77& 0.76 \\
 Senegal & Random &0.79 & 0.79& 0.79& 0.79& 0.82 \\
 Indonesia & Random &0.80 & 0.81& 0.78& 0.79& 0.77  \\
 Colombia &  Spatial & \textbf{0.31} & \textbf{0.34}  & \textbf{0.32} & \textbf{0.34} & \textbf{0.34}  \\
 Madagascar & Spatial & \textbf{0.65} & 0.74& 0.70& 0.75 & 0.76   \\
 Senegal & Spatial & 0.85 & \textbf{0.91}& 0.85& \textbf{0.94} & 0.85  \\
  Indonesia & Spatial & 0.80 & 0.78& 0.78& 0.76& 0.75  \\
\end{tabular}
\label{t:results2}
\end{table}

>>>>

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. Values outside 0.7--0.9 are shown in bold.}
\centering
\begin{tabular}{llrrrrr}
Country &  CV & Enviro & ML\textsubscript{l} &  Enviro + ML\textsubscript{l} & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random & \textbf{0.28} & \textbf{0.28} & \textbf{0.29} & \textbf{0.29} & \textbf{0.29} \\
 Madagascar &  Random & 0.80 & 0.77& 0.75& 0.77& 0.76 \\
 Senegal & Random &0.79 & 0.79& 0.79& 0.79& 0.82 \\
 Indonesia & Random &0.80 & 0.81& 0.78& 0.79& 0.77  \\
 Colombia &  Spatial & \textbf{0.31} & \textbf{0.34}  & \textbf{0.32} & \textbf{0.34} & \textbf{0.34}  \\
 Madagascar & Spatial & \textbf{0.65} & 0.74& 0.70& 0.75 & 0.76   \\
 Senegal & Spatial & 0.85 & \textbf{0.91}& 0.85& \textbf{0.94} & 0.85  \\
  Indonesia & Spatial & 0.80 & 0.78& 0.78& 0.76& 0.75  \\
\end{tabular}
\label{t:results2}
\end{table}

\begin{table}
\caption{Fitted regression parameters of the environmental and machine learning covariates for thee models: just environmental variables, just local machine learning models and the combination of the two.}
\centering
\tiny
\begin{tabular}{ll|rrr}
Country    & Variable &  $\beta_{enviro}$   & $\beta_l$ & $\beta_{enviro+l}$\\ \hline
Madagascar & LST mean & 0.17 &  &  -0.01\\
Madagascar & EVI & 0.32 &  & -0.04 \\
Madagascar & TSI & 0.42 &  &0.06  \\
Madagascar & access & 0.34 &  &0.00  \\
Madagascar & Elev & -0.14 &  & 0.00\\ 
Madagascar & LST sd & -0.78 &  &-0.04  \\
Madagascar & VIIRS & -0.1 &  &-0.52  \\
Madagascar & TCW & -0.22 &  & -0.06\\ 
Madagascar & RF &  & 0.29 &  0.01\\
Madagascar & GBM &  & 0.52 & 0.25 \\
Madagascar & enet &  & 0.31 &0.09  \\
Madagascar & nnet &  & 0.43 &0.14  \\
Madagascar & ppr &  & 0.49 & 0.22\vspace{0.2cm}\\ 
Colombia & LST mean &-0.12  &  & -0.22\\
Colombia & EVI &  -0.08&  & 0.17\\
Colombia & TSI &  0.54&  & -0.06\\
Colombia & access &  0.35&  &0.00 \\
Colombia & Elev &  0.47&  & 0.00\\
Colombia & LST sd & -0.11 &  & -0.10\\
Colombia & VIIRS & 0.24 &  & 0.01\\
Colombia & TCW &  0.21&  & 0.00\\
Colombia & RF &  & 0.36 & -0.18\\
Colombia & GBM &  & 0.54 & 0.26\\
Colombia & enet &  & 0.32 & -0.34\\
Colombia & nnet &  &0.33  & -0.09\\
Colombia & ppr &  & 0.54 & 0.01\vspace{0.2cm}\\
Senegal & LST mean &-0.04  &  &-0.02\\
Senegal & EVI &  0.33&  & 0.30\\
Senegal & TSI &  -0.58&  &  -0.59\\
Senegal & access & -0.03 &  &  -0.05\\
Senegal & Elev &  0.42&  &0.37\\ 
Senegal & LST sd &  0.21&  & 0.10 \\
Senegal & VIIRS &  0.13&  &  0.13\\
Senegal & TCW & 0.08 &  &-0.01\\ 
Senegal & RF &  & 0.34 &  0.20\\
Senegal & GBM &  &  0.28& 0.05\\
Senegal & enet &  &  0.27&  -0.05\\
Senegal & nnet &  & 0.29 &-0.09 \\
Senegal & ppr &  &  0.35& 0.25\vspace{0.2cm}\\
Indonesia & LST mean & -0.32 &  &-0.34\\
Indonesia & EVI &  0.49&  & 0.36\\
Indonesia & TSI &  0.58&  &0.52\\
Indonesia & access &0.33 &  & 0.06 \\
Indonesia & Elev& -0.06&  &-0.13\\ 
Indonesia & LST sd & -0.23 &  & -0.33\\
Indonesia & VIIRS &  -0.12&  & 0.03\\
Indonesia & TCW& 0.12 &  &0.10\\ 
Indonesia & RF &  & 0.32 & 0.06\\
Indonesia & GBM &  &  0.38&0.03\\
Indonesia & enet &  &  0.49&  0.56\\
Indonesia & nnet &  &  0.36&  0.18\\
Indonesia & ppr &  &  0.45& 0.32\\
